Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Add higher-order functions
Add related work

But what if the design of the type system is unclear?  \citet{tip} propose
an intriguing approach called trace typing. With trace typing, a new type
system can be prototyped and evaluated by applying the type rule to
execution traces of programs. While the approach has the limitation of
dynamic analysis techniques, namely that the results are only as good at the
coverage of the source code, it allows to quickly test new design and
quantify how much of a code base can be type-checked.  Other approaches that
infer types for dynamic analysis include the work of \citet{FurrAF2009} for
Ruby.

@@

>>>>

But what if the design of the type system is unclear?  \citet{tip} propose
an intriguing approach called trace typing. With trace typing, a new type
system can be prototyped and evaluated by applying the type rule to
execution traces of programs. While the approach has the limitation of
dynamic analysis techniques, namely that the results are only as good at the
coverage of the source code, it allows to quickly test new design and
quantify how much of a code base can be type-checked.  Other approaches that
infer types for dynamic analysis include the work of \citet{FurrAF2009} and
\citet{hicks2011ruby} for Ruby.

@@

\paragraph{Higher-Order Functions}
\typetracer assigns the type \CLASS{\texttt{function}} to function values.
The number of positions that receive a function is 1,831, which is just
2\% of all the positions for which we infer types. Given the small number of
occurrences, it is not worth complicating the inferred types with a complete
signature for these functions.
